Reanalysis Step 4: Outcome Analysis with Three-Way Interaction

### 2025-08-20 reanalysis-4-outcome_analysis.qmd
wip

# Create interaction plot with Odds Ratios (converted from log odds)
p1 <- ggplot(plot_data, aes(x = DR_Severity, y = OR, 
                            color = Treatment, group = Treatment)) +
  geom_point(size = 3) +
  geom_line(size = 1) +
  geom_errorbar(aes(ymin = OR_CI_Lower, ymax = OR_CI_Upper), 
                width = 0.1, size = 0.8) +
  geom_hline(yintercept = 1, linetype = "dashed", alpha = 0.5) +
  labs(title = "Three-Way Interaction: Lapse × DR Severity × Treatment",
       subtitle = "Effect of lapsing on vision impairment (odds ratio scale)",
       x = "DR Severity",
       y = "Odds Ratio",
       color = "Treatment Status") +
  theme_minimal() +
  theme(plot.title = element_text(size = 14, face = "bold"),
        axis.text = element_text(size = 11),
        axis.title = element_text(size = 12),
        legend.position = "bottom") +
  scale_color_manual(values = c("No_Treatment" = "#2ca02c", 
                               "Any_Treatment" = "#d62728")) +
  scale_y_continuous(breaks = seq(0, ceiling(max(plot_data$OR_CI_Upper)), 0.5))

>>>>

# Create interaction plot with Odds Ratios (converted from log odds)
p1 <- ggplot(plot_data, aes(x = DR_Severity, y = OR, 
                            color = Treatment, group = Treatment)) +
  geom_point(size = 3) +
  geom_line(size = 1) +
  geom_errorbar(aes(ymin = OR_CI_Lower, ymax = OR_CI_Upper), 
                width = 0.1, size = 0.8) +
  geom_hline(yintercept = 1, linetype = "dashed", alpha = 0.5) +
  labs(title = "Three-Way Interaction: Lapse × DR Severity × Treatment",
       subtitle = "Effect of lapsing on vision impairment (odds ratio scale)",
       x = "DR Severity",
       y = "Odds Ratio",
       color = "Treatment Status") +
  theme_minimal() +
  theme(plot.title = element_text(size = 14, face = "bold"),
        axis.text = element_text(size = 11),
        axis.title = element_text(size = 12),
        legend.position = "bottom") +
  scale_color_manual(values = c("No_Treatment" = "#2ca02c", 
                               "Any_Treatment" = "#d62728"))
